%%%% ijcai19.tex

\typeout{IJCAI-19 Instructions for Authors}

% These are the instructions for authors for IJCAI-19.

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai19.sty is NOT the same than previous years'
\usepackage{ijcai19}

% Use the postscript times font!
\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{array}
\urlstyle{same}
% the following package is optional:
%\usepackage{latexsym} 

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.

% \title{Social Relationship Detection using Rules}

\title{Understanding social relationship with person-pair relations}

% Single author syntax
\author{
    Sarit Kraus
    \affiliations
    Department of Computer Science, Bar-Ilan University, Israel \emails
    pcchair@ijcai19.org
}

% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
% Check the ijcai19-multiauthor.tex file for detailed instructions
\iffalse
\author{
First Author$^1$
\and
Second Author$^2$\and
Third Author$^{2,3}$\And
Fourth Author$^4$
\affiliations
$^1$First Affiliation\\
$^2$Second Affiliation\\
$^3$Third Affiliation\\
$^4$Fourth Affiliation
\emails
\{first, second\}@example.com,
third@other.example.com,
fourth@example.com
}
\fi

\begin{document}

\maketitle

\begin{abstract}
% Social relationships play a very important role in social network. Social relationship understanding has attracted increasing attention, typically, which can help to understand the behavior of humen in our daily life. Previous social relationship understanding models focused too much on relationships between the same pair and ignore the interplay of different relationships in the same scene.  We found that the interaction between the relationships in the same scene plays an important role in the understanding of social relations and we can make meanful use of rules during inference. This paper proposes a novel model named {\it SRDR} which incorporates rules seamlessly into the deep learning model named {\it SR}  to solve the social relationship understanding problem. It formulates inference as an integer linear programming (ILP) problem, with the objective function generated from {\it SR} and the constraints translated from rules. By incorporating rules, our approach can greatly reduce the solution space and significantly improve the inference accuracy of social relationship understanding models. Experimental results on two classic data sets show that our approach significantly outperforms state-of-the-art  models in social relationship understanding, which justifies the significance of incorporating rules seamlessly into the deep learning model in social relationship understanding task.

Social relationships understanding is to infer the relations among people from images and videos, which has attracted increasing attention in computer vison recently. A great progress has been made since the rise of deep learning. However, they mostly focuses on the facial attributes or contextual objects cues without taking into account the interaction among person pairs. Motivated by scene graph generation, we carefully studied the datasets and found the social relations in a still image always have high semantic relevance. For instance, if two person pair in an image are {\it Friends}, then the third one is always friends or at least other {\it Intimate} relations but not {\it No Relation}. Therefore, to capture this interaction cues, we propose a novel end-to-end trainable Person-Pair Relation Network (PRN) using standard RNNs, a graph inference network that learns iteratively to improve its predictions via message passing among person pair nodes. Extensive experiments on PISC and PIPA-Relation show the superiority of our method over previous methods. 

\end{abstract}

\section{Introduction}
Social relationships are closely related to our daily life \cite{DBLP:conf/wacv/BarrCBF14}. After understanding the social relationship between the person pair, we can easily explain their behavior. For machines, only when they fully understand the social relationships, can they further understand and infer the human behavior in our social life, so as to make a better response.

This part will be written by {\bf liangjinrui} . This part will consist of the following sections:
\begin{itemize}
	\item The significance of social relation understanding
	\item {\bf [Example Figure]}
	\item Analyze the shortcomings of the current model and introduce our model(based ILP)
	\item Challenges
	\item Contributions
\end{itemize}

\section{Related Work}

This part will be written by {\bf liangjinrui} and it will be surveyed by {\bf liangjinrui} and {\bf chenhaicheng} by January 31.

\subsection{Social Relationship Understanding}
% Introduce social relationship understanding including \cite{DBLP:conf/aaai/GuoWWWG18}, \cite{DBLP:conf/iccv/LiWZK17}, \cite{DBLP:conf/ijcai/WangWG15} and \cite{DBLP:conf/ijcai/WangCRYCL18}.

The foundation of social network is the social relationships understanding, an important multidisciplinary problem that has attracted increasing attention in computer vision recently. A much number of studies that aim to infer social relationships from images \cite{DBLP:conf/ijcai/WangWG15,DBLP:conf/iccv/LiWZK17,DBLP:conf/ijcai/WangCRYCL18,DBLP:conf/eccv/WangGLF10,DBLP:conf/iccv/ZhangLLT15} and videos \cite{DBLP:conf/eccv/DingY10,DBLP:conf/cvpr/RamanathanY013,DBLP:journals/ivc/VinciarelliPB09} have been made since the rise of deep learning. For instance, motivated by psychological sudies, \cite{DBLP:conf/iccv/ZhangLLT15} and \cite{DBLP:conf/iccv/DibekliogluSG13} exploit social relationships based on facial attributs such as expression and head pose, and affective behaviour analysis. Besides, \cite{DBLP:conf/iccv/LiWZK17} and \cite{DBLP:conf/ijcai/WangCRYCL18} discover that contextual cues around people play a significant role in social realtionship infering. Concretely, \cite{DBLP:conf/iccv/LiWZK17} proposed a dual-glance model for social relationship, where the first glance makes a coarse relationship prediction for a given person pair and then the second one refines the prediction by using the objects around the pair. \cite{DBLP:conf/ijcai/WangCRYCL18} build a knowledge graph and employed Gated Graph Neural Network (GGNN) \cite{DBLP:journals/tomccap/LiSKJZW15} to integrate the graph into the Graph Reasoning Model (GRM), a deep neural network where a proper message propagation and graph attention mechanism are introduced to explore the interaction between person pair and the contextual objects.

Unlike the aforementioned works which mainly focus on facial attributs or contextual object cues, we detaily studied the two classic datasets PISC \cite{DBLP:conf/iccv/LiWZK17} and PIPA-relation \cite{DBLP:conf/cvpr/SunSF17} and found the social relations in a still image have high semantic relevance. Based on this discovery, we designed a novel end-to-end trainable Person-Pair Relation Network (PRN), a graph inference network to capture this semantic relevance cues via message passing among person pair nodes.

\subsection{Message Passing}%


Introduction to Message Passing, written by {\bf liangjinrui}.
 


\subsection{Rules and ILP}

Introduce rules and ILP referring to \cite{DBLP:conf/ijcai/WangWG15}



\section{Model}
This part will be written by {\bf liangjinrui} and {\bf chenhaicheng}.
{\bf [model figure]}

[Introduce the total model]

In this section, we introduce the proposed person-pair relational network for social relationship understanding. We fomulate the relationshipes of an image as a social graph, and followed\cite{DBLP:conf/ijcai/WangCRYCL18}
to extract various features. Then, These features are used to initialize the nodes on the social graph. Person pair relation network employs Gated Recurrent Unit\cite{DBLP:conf/ssst/ChoMBB14} to explore the interaction of relationships with each other, and we employ the attention mechanism to adaptively exploit the most relevant nodes. It integrates multiple
component to learn the representations of relationshipes between peoples in an image. 
 The proposed framework is shown in Fig. 2.

\subsection{Visual Appearance and Spatial Cue} \label{section:vs}

Given an image \textbf{I} and the bounding box of peoples, we first crop three patches for each person pair, where the first two cover each person, $\mathbf{p_1}$ and $\mathbf{p_2}$, and one for union region, $\mathbf{p_u}$, that cover the both people and maintains the basic informantion for recognition. These patches are resized to 224 \times 224 pixels and fed into three CNNs, These feature vectors from the last convolutional layer are flattened and concatenated. $\textbf{p_1}$ and $\textbf{p_2}$ share the same weights. In addition, the geometry feature of bounding box is complementary to the visual appearance. 

\subsection{Reasoning of Recurrent Neural Network}

\subsection{Message pooling} \label{section:mp}

we formulate the 

\ref{section:vs} provides 





\section{Experiments}

This part will be written by {\bf chenhaicheng}.
\subsection{Experiment Setting}

{\bf Datasets.} In this work, two datasets were used to evaluate our proposed method and other existing ones. The first one is the large-scale People in Social Context (PISC) \cite{DBLP:conf/iccv/LiWZK17} with 22,670 images and contains two-level recognition tasks: {\bf 3 Coarse-level relationship}, namely {\it No Relation, Intimate Relation, None-Intimate Relation} and {\bf 6 Fine-level relationship}, i.e., {\it Friend, Family, Couple, Professional, Commerical, No Relation}. The second one is the People in Photo Album Relation (PIPA-Relation) \cite{DBLP:conf/cvpr/SunSF17}, an extension verson of People in Photo Album (PIPA) \cite{DBLP:conf/cvpr/ZhangPTFB15} with 37107 images. It also annotates 26,915 person pairs on two-level recognition tasks: {\bf 5 Social Domains} and {\bf 16 Social Relations} based on these domains. The train/val/test in PISC are 13,142/4,000/4,000 images with 14,536/25,636/15,497 person pairs on coarse level relationship, and 16,828/500/1,250 images with 55,400/1,505/3,691 person pairs on fine level relationshp, respectively. In PIPA-relation, we follow \cite{DBLP:conf/ijcai/WangCRYCL18} and focus on recognizing its 16 relationships in the experiment. The train/val/test in it are 13,729/709/5,106 person pairs.\\
{\bf Implementation Details.} During our work, We adopt the same strategy as previous works including \cite{DBLP:conf/iccv/LiWZK17} and \cite{DBLP:conf/ijcai/WangCRYCL18}. First, we fine-tune the ResNet-101 model \cite{DBLP:conf/cvpr/HeZRS16} , and we set the a lower learning rate as 0.0001. For the message passing progation model, the dimension of hidden size is set as 512. The iteration time T is set as 4 and learning rate as 0.0001. Similer to \cite{DBLP:conf/ijcai/WangCRYCL18}, we the fine-tuning model utilized SGD, and the message passing module is trained with ADAM.


\subsection{Comparisons with State-of-the-Art Methods}

we compare our proposed model with existing state-of-the-art methods on both PISC and PIPA-Relation datasets.Formally, the compared methods are as followed:
\subsubsection{Performance on the PISC dataset}
{\bf UnionCNN}  Following \cite{DBLP:conf/eccv/LuKBL16}, it generates a single CNN model to predicate relations. In this task, we also feeds the union region of person pair to s single CNN for classification.\\
{\bf Pair CNN}\cite{DBLP:conf/iccv/LiWZK17} consists of two equivalent CNNs with shared weights to extracted features for image for two individuals.\\
{\bf Pair CNN + BBox + Union}\cite{DBLP:conf/iccv/LiWZK17} incorporates spatial location information of two bounding box that based the previous pair CNN and Union CNN.\\
{\bf Dual-glance}\cite{DBLP:conf/iccv/LiWZK17} implements coarse and fine prediction which includes three and six relationships. Dual-glance employing pair CNN + BBox + BBox + Union and utilized surrounding region proposal to refine the prediction.\\
{\bf GRM}\cite{DBLP:conf/ijcai/WangCRYCL18} propse a graph reasoning model that unifies the frequence of co-concurrences of each relationship-object pair to facilitate social relation.

Similar to the model of GRM, we also adopt the per-class recall and mean average precision(mMP) to evaluate our model. The experiments data are reported in Table 1. First, both Pair CNN + BBox + Union, Pair CNN + BBox + Global, Dual-glance are incur extra Faster-RCNN\cite{DBLP:conf/nips/RenHGS15} to extract the local contextual cues(object proposal). GRM utilized the object proposal to construct a semantic-aware  knowledge graph to reason about the social relationship. It is notable that both of them incur extra detection annotations that contains noises.

\subsection{Experiment Results}

\begin{table*}[htpb]
  \centering
  \caption{Recall-per-class and mean average precision (mAP) evaluating our PRN model and previous methods on PISC}
  \label{tab:label}
  \begin{tabular}{c|p{0.5cm}<{\centering}|p{0.5cm}<{\centering}|p{0.5cm}<{\centering}|p{0.5cm}<{\centering}||p{0.5cm}<{\centering}|p{0.5cm}<{\centering}|p{0.5cm}<{\centering}|p{0.5cm}<{\centering}|p{0.5cm}<{\centering}|p{0.5cm}<{\centering}|p{0.5cm}<{\centering}}
    \hline
    \multirow{2}{*}{Methods} & \multicolumn{4}{c|}{Coarse relationships} & \multicolumn{7}{|c}{Fine relationships} \\
    \cline{2-12}
    ~ & \rotatebox[origin=l]{90}{Intimate} & \rotatebox[origin=l]{90}{Non-Intimate} & \rotatebox[origin=l]{90}{No Relation} & \rotatebox[origin=l]{90}{mAP} & \rotatebox[origin=l]{90}{Friends} & \rotatebox[origin=l]{90}{Family} & \rotatebox[origin=l]{90}{Couple} & \rotatebox[origin=l]{90}{Professional} & \rotatebox[origin=l]{90}{Commerical} & \rotatebox[origin=l]{90}{No Relation} & \rotatebox[origin=l]{90}{mAP} \\
    \hline\hline
    Union CNN \cite{DBLP:conf/eccv/LuKBL16} & 72.1 & 81.3 & 19.2 & 58.4 & 29.9 & 58.5 & 70.7 & 55.4 & 43.0 & 19.6 & 43.5 \\
    Pair CNN \cite{DBLP:conf/iccv/LiWZK17} & 70.3 & 80.5 & 38.8 & 65.1 & 30.2 & 59.1 & 69.4 & 57.5 & 41.9 & 34.2 & 48.2 \\
    Pair CNN + BBox + Union \cite{DBLP:conf/iccv/LiWZK17} & 71.1 & 81.2 & 57.9 & 72.2 & 32.5 & 62.1 & 73.9 & 61.4 & 46.0 & 52.1 & 56.9 \\
    Pair CNN + BBox + Global \cite{DBLP:conf/iccv/LiWZK17} & 70.5 & 80.0 & 53.7 & 70.5 & 32.2 & 61.7 & 72.6 & 60.8 & 44.3 & 51.0 & 54.6 \\
    Dual-glance \cite{DBLP:conf/iccv/LiWZK17} & 73.1 & 84.2 & 59.6 & 79.7 & 35.4 & 68.1 & 76.3 & 70.3 & 57.6 & 60.9 & 63.2 \\
    \hline
    Ours & & & & & & & & & & & \\
    \hline
  \end{tabular}
\end{table*}

\subsubsection{Performance on the PIPA-Relation dataset}
On this dataset, we also compare our proposed model with the existing Two stream CNN\cite{DBLP:conf/cvpr/SunSF17},Dual-glance\cite{DBLP:conf/iccv/LiWZK17} and GRM\cite{DBLP:conf/ijcai/WangCRYCL18}.As the current dataset of PIPA-relation, Dual-glance and GRM achieves the best performance. Specifically, we directly reprint the experimental of serveral baselines from the literature. The Result are presented in Table 2. Notably, our PRN sigmificantly outperforms previous methods. Specifically, it is comparabel of our proposed model with previous model, and beating the best of them 2.4\%.  
\subsection{Analysis on Experimental result}

In this section, we first present the comparison result  of message passing mechanism and analsis the reasons behind, and the result present in Table 3.
Then, we conduct a conditional experiment to investigate the effectiveness of 
the factor of region contexuals and the interaction between person-pair.
\subsubsection{Significance of message passing}

In our framework, the core component is the introduction of message passing mechanism, and one of the key component is the message pooling functions that use learnt weights sum to aggregate hidden state of other relation nodes into message. To futher inverstigate the improvement of our approach on recognizing social relationships, we evaluate variants of our model
with standard pooling methods. The first is to use average-pooling (avg. pool) instead of the learnt weighted sum to
aggregate the hidden states. The second is similar to the first
one, but uses max-pooling (max pool).

\subsubsection{Analysis of contextual relationships and contexual regions}

First, our model is to process the cue of contexual relationships without contextual region that incured in Dual-glance and GRM by extra detecion annotation. As preceding mentioned, the scene of an image is stable and the sementic relationship of all the person pair tends to be similar.
 \cite{DBLP:conf/iccv/LiWZK17} trained a RCNN with attention machanisms to exploit different contextual cues according different pairs of people. we also conduct a attention machanisms as same as Dual-glance, but the performance do not improved as reported in Table 3. For example, if the object of laptop is useful to classifier the relationship as professional, but  the detection model does not always achieve this. One possible reason is that the contexual regions cues is coverd by contexual relationships cues.


\begin{table}[htb]
	\vspace*{-7.5pt}
	\centering
	\caption{The mMap and accuracy result of RCNN, our model and our model with contexual region that implements in the same way as dual-glance}
	\vspace*{0.1cm}
	\scalebox{1}{
		\begin{tabular}{c|c|c|c|c}
			\toprule
			\multirow{2}{*}{Multi-Row} &
			\multicolumn{2}{c|}{Multi-Column} &
			\multicolumn{2}{|c}{Multi-Row}  \\
 				 & column-1 & column-2 & 3 & 4  \\
			\hline
			RCNN & - & 63.5 & - & 48.4 \\
			\hline
			Ours & label-2 & label-3 & label-4 & label-5 \\
			\hline
			Ours+region & label-2 & label-3 & label-4 & label-5 \\
		\end{tabular}
	}
\end{table}

\subsection{Ablation Study}


\subsection{Case Study}

\section{Conclusion}
This part will be written by {\bf liangjinrui}.

\newpage
%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{ijcai19}

\end{document}
